\PaperTitle

### 2024-05-02 Final_Report/paper.tex
Added in some subsections and descriptioons for sections 2 and 3.

\section{Proposed Method}

\section{Evaluation}

>>>>

\section{Proposed Method}
This section presents the methodology for how this project goes about capturing network packet data, analyzing the data, and classifying it based on its website of origin.

\subsection{Capturing Data}
\subsection{Data Preparation and Processing}
\subsection{Employed models}
\section{Evaluation}
This section comprehensively evaluates our models and their performance on the dataset and validating sets.
\subsection{Dataset}
